\documentclass[12pt,letterpaper]{article}
\begin{titlepage}
\begin{document}
\begin{center}
\title{COLLEGE OF COMPUTING AND INFORMATION SCIENCES\\ DEPARTMENT OF COMPUTER SCIENCE\\ SCHOOL OF COMPUTING AND INFORMATICS TECHNOLOGY\\}
\maketitle
\end{center}
\begin{flushleft}
\begin{center}
\title{NAME:	     SSENYONGA RICHARD SEMPEWO\\
STUDENTS NUMBER:	 214004470\\
REGISTRATION NUMBER: 14/U/14991/EVE}
\maketitle
\end{center}
\end{flushleft}
\end{titlepage}
 \begin{center}
  \line(1,0){300}\\
  [0.25in]
  \huge{\bfseries A REPORT ABOUT  A RESTAURANT BUSINESS IN BWAISE REGION}\\
  [2mm]
  \line(1,0){200}\\
  \maketitle
  \end{center}
  \section{INTRODUCTION}
  Maama Kato is a franchise restaurant located in Bwaise region along Bombo road that specializes in providing its customers a fresher alternative to typical food products with convenience. The restaurant is positioned between traditional foods and the western type of foods. According to research data from Kampala city authority customers are more attuned to the health benefits of theirs eating habits and are willing to pay more for better food choice when compared to the general population. Different food products are to be provided to our customers regardless of their culture or origin.
  
\section{BACKGROUND}
Due to the on going developments around Bwaise region and mainly along Bombo road ,there was need to set up a quality restaurant  in the area. This gave birth to idea set up of Maama Kato restaurant within the area to relive of the hustles and hurdles of finding a good meal within the area. The restaurant was set up provide better food and affordable meals than its competitors. The restaurant  market target is the young adults, families and tourists within the Bwaise. The young adults in this case have the potential of providing large volumes sales to the restaurant during peak hours of the day of 11am to 2 pm since that is the time when they have a break from their respective activities. The families are also a growing population and  the restaurant will be a convenient choice for families which rarely have time to prepare their own meals.
The restaurant will provide a variety of meals ranging from traditional to western  meals in the case of its tourist population. The traditional meals will include foods from  the east ,the west ,the north and central since the restaurant is to provide a warm and friendly environment to its customers.
The restaurant as earlier said is located is Bwaise since the area is under going numerous developments and for this reason good hub for a food business felt with ambience and relaxation to its customers within the customers.

\section{BUSINESS OBJECTIVES}
The mission of Maama Kato restaurant is to provide people high quality, healthy meals at reasonable price. We pledge to provide clean seating with a good view of the main features within the areas. Customers can be sure their food will be good and the service friendly and very fast. Other objectives of the restaurant include;

- Providing quality meals at affordable prices.	
- Providing relaxing dining experience for customers.
- Providing warm friendly services to customers

\section{CONCLUSION}
 In conclusion therefore Maama Kato restaurant is to be set up to reduce flux of people having their meals in untidy places without friendly services in the Bwaise area.
\end{document}\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
•
\end{document}
